\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-22 paper/main.tex

\subsubsection{Hyperparameter tuning}
As the number of drug-targets are sparse with respect to the number of
both drugs and proteins considered, the training, validation and
testing datasets are imbalanced. As there are only $22,336$ links in
the considered subset the ratio
\begin{equation}
	w:= \frac{\#drugs \cdot \#proteins}{\#dti\_links} \approx 360,
	\label{weight}
\end{equation}
and consequently needs to be compensated in the computed loss function
and appropriate metrics for the evaluation.

>>>>

\subsubsection{Hyperparameter tuning}
As the number of drug-targets are sparse with respect to the number of
both drugs and proteins considered, the training, validation and
testing datasets are imbalanced. As there are only $22,336$ links in
the considered STITCH subset, the ratio
\begin{equation}
	w:= \frac{\#drugs \cdot \#proteins}{\#dti\_links} \approx 360,
	\label{weight}
\end{equation}
consequently needs suitable compensation in the computed loss function and
appropriate metrics for the evaluation.
